\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=18mm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}

\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=1pt,parsep=0pt}

\titlespacing*{\section}{0pt}{8pt}{2pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\hypersetup{
  colorlinks=true,
  urlcolor=blue!50!black,
  linkcolor=blue!50!black,
}

\pagestyle{empty}

\newcolumntype{R}{>{\raggedleft\arraybackslash}p{0.22\textwidth}}

\begin{document}

\begin{center}
{\LARGE\bfseries Takeshi Tsukada}\\[3pt]
Professor, Graduate School of Science, Chiba University\\[2pt]
Email: \href{mailto:t.tsukada@acm.org}{t.tsukada@acm.org}
\quad\textbar\quad
Web: \href{https://takeshi-tsukada.github.io}{https://takeshi-tsukada.github.io}
\end{center}

\section*{Appointments}
\begin{tabularx}{\textwidth}{@{}XR@{}}
Professor, Graduate School of Science, Chiba University & Oct.\ 2024 -- present \\
Associate Professor, Graduate School of Science, Chiba University & Sep.\ 2020 -- Sep.\ 2024 \\
Assistant Professor, Graduate School of Information Science and Technology, The University of Tokyo & Apr.\ 2015 -- Aug.\ 2020 \\
JSPS Overseas Research Fellow, University of Oxford (host: C.-H.\ Luke Ong) & Oct.\ 2013 -- Mar.\ 2015 \\
Postdoctoral Researcher, The University of Tokyo (host: Naoki Kobayashi) & Apr.\ 2013 -- Sep.\ 2013 \\
\end{tabularx}

\section*{Education}
\begin{tabularx}{\textwidth}{@{}XR@{}}
Ph.D.\ in Information Science, Tohoku University & Mar.\ 2013 \\
M.Sc.\ in Information Science, Tohoku University & Mar.\ 2010 \\
B.Eng., Kyoto University & Mar.\ 2008 \\
\end{tabularx}

\section*{Honors and Awards}
\begin{itemize}
  \item \textbf{ACM SIGPLAN Distinguished Paper Award}, POPL 2025 \\
        for ``A Primal-Dual Perspective on Program Verification Algorithms''
  \item \textbf{EATCS Best Paper Award at ETAPS}, FoSSaCS 2014 \\
        for ``Unsafe Order-2 Tree Languages Are Context-Sensitive''
\end{itemize}

\section*{Selected Publications}
\begin{itemize}
  \item Takeshi Tsukada, Hiroshi Unno, Oded Padon, and Sharon Shoham.
        ``A Primal-Dual Perspective on Program Verification Algorithms.''
        \emph{Proc.\ ACM Program.\ Lang.}\ (POPL), 2025.
  \item Takeshi Tsukada and Hiroshi Unno.
        ``Inductive Approach to Spacer.''
        \emph{Proc.\ ACM Program.\ Lang.}\ (PLDI), 2024.
  \item Takeshi Tsukada and Kazuyuki Asada.
        ``Enriched Presheaf Model of Quantum FPC.''
        \emph{Proc.\ ACM Program.\ Lang.}\ (POPL), 2024.
  \item Yu Gu, Takeshi Tsukada, and Hiroshi Unno.
        ``Optimal CHC Solving via Termination Proofs.''
        \emph{Proc.\ ACM Program.\ Lang.}\ (POPL), 2023.
  \item Takeshi Tsukada and Hiroshi Unno.
        ``Software Model-Checking as Cyclic-Proof Search.''
        \emph{Proc.\ ACM Program.\ Lang.}\ (POPL), 2022.
  \item Naoki Kobayashi, Takeshi Tsukada, and Keiichi Watanabe.
        ``Higher-Order Program Verification via HFL Model Checking.''
        In \emph{Proc.\ of ESOP}, 2018.
  \item Naoki Kobayashi, Kazuhiro Inaba, and Takeshi Tsukada.
        ``Unsafe Order-2 Tree Languages Are Context-Sensitive.''
        In \emph{Proc.\ of FoSSaCS}, 2014.
\end{itemize}

\section*{Professional Service}
\textbf{Program committees:} POPL 2026; CSL 2025; LICS 2025; PPL 2025 (co-chair); ESOP 2024; MFCS 2024; ICFP 2023; ICALP 2023; LICS 2021; APLAS 2019; FSCD 2019.

\textbf{Society committees:} Secretary, IPSJ SIG on Programming (SIGPRO), 2024 -- present; Steering Committee Member, IPSJ SIG on Programming (SIGPRO), 2019 -- 2023; Steering Committee Member, JSSST SIG on Programming Theory, 2025 -- present.

\section*{Research Interests}
Programming language theory; game semantics; automated verification; higher-order model checking; type systems.

\end{document}
